SciPy - some descriptive title here

### 2018-06-27 scipy-1.0/paper.tex
ENH: add some authors and a title for manuscript.
Remove duplicated author
ENH: first draft of abstract for SciPy paper.

\begin{abstract}
TODO. Abstract must be under 200 words and not include subheadings or citations.
\end{abstract}
\begin{document}

>>>>

\begin{abstract}
SciPy is an open source scientific computing library for the Python programming language.
SciPy 1.0 was released in late 2017, about 16 years after the original
version 0.1 release. SciPy
has become a \emph{de facto} standard in the community, with more than 600
unique code contributors and millions of downloads per year, despite
the absence of an official project publication, until now. The library
includes functionality spanning clustering, Fourier transforms,
integration, interpolation, file I/O, linear algebra, image processing,
orthogonal distance regression, minimization algorithms, signal processing,
sparse matrix handling, computational geometry, and statistics. In this
work, we highlight some recent technical developments and provide
an overview of the capabilities and development practices of the
SciPy library.
\end{abstract}
\begin{document}
